Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-05-10 Master Thesis/synopsis.tex
Add lemma for defectless valuations

@@

\begin{proof}
Assume that $K$ is not algebraically closed. $w_1$ and $w_2$ can't be trivial, for otherwise $\dim k(w_i)=\dim (K)\neq 0$. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are dependent. Since two different valuations of rank $1$ are independent, at least one of $w_1$ and $w_2$ is of rank $2$. Now, let's assume that $w_1$ is of rank $1$ and $w_2$ is of rank $2$. Since they are dependent, it follows $v(w_2) = w_1$ and $w_1$ has a non-trivial specialization, a contradiction to $w_1\in |\operatorname{Spv}(K)|$.

>>>>

\begin{lemma}\phantomsection\label{lemma-defectless-valuations}
\begin{enumerate}[(i)]
\item $\operatorname{Spv}_\text{d}^{(1)}(K) = \operatorname{Spv}_\text{rd}^{(1)}(K)$
\item $\operatorname{Spv}^{(2)}(K) = \operatorname{Spv}_\text{d}^{(2)}(K)$
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}[(i)]
\item Let $v$ be a defectless valuation of rational rank $1$. By Lemma \ref{rank-dimension-inequality}, $\operatorname{rank}(v) \leq \operatorname{rrank}(v) = 1$. Since $\Gamma_v$ is not trivial, $\operatorname{rank}(v) = 1=\operatorname{rrank}(v)$.
\item Let $v$ be a valuation of rational rank $2$. Due to Lemma \ref{rank-dimension-inequality}, the dimension inequality is an equality. \qedhere
\end{enumerate}
\end{proof}

@@

\begin{proof}
Assume that $K$ is not algebraically closed. $w_1$ and $w_2$ can't be trivial, for otherwise $\dim k(w_i)=\dim (K)\neq 0$. By the Theorem of F.K. Schmidt \ref{theorem-fkschmidt}, we can see that $w_1,w_2$ are dependent. Since two different valuations of rank $1$ are independent, at least one of $w_1$ and $w_2$ is of rank $2$. Now, assume that $w_1$ is, say, of rank $1$ and $w_2$ is of rank $2$. Since they are dependent, it follows $v(w_2) = w_1$ and $w_1$ has a non-trivial specialization, a contradiction to $w_1\in |\operatorname{Spv}(K)|$.
